A patch-based framework for new ITK functionality: Joint fusion, denoising, and non-local super-resolution

### 2017-03-13 Document/LaTeX/ArticleExample.tex
ENH:  Refactoring.

% The title should be descriptive enough for people to be able to find
% the relevant document.
\title{Two Luis Miguel fans walk into a bar in Nagoya $\xRightarrow[]{yada\,\,\,yada\,\,\,yada}$
an ITK-implementation of a popular patch-based denoising filter}

%
% NOTE: This is the last number of the "handle" URL that
% The Insight Journal assigns to your paper as part of the
% submission process. Please replace the number "1338" with
% the actual handle number that you get assigned.
%
\newcommand{\IJhandlerIDnumber}{3564}

@@

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Nick Tustison$^{1}$ and Jose Vicente Manj\'on$^{2}$}
\authoraddress{$^{1}$University of Virginia, Charlottesville, VA\\
               $^{2}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
               }

@@

% The abstract should be a paragraph or two long, and describe the
% scope of the document.
\begin{abstract}
\noindent
This document describes an ITK implementation of the adaptive patch-based
image denoising algorithm described in \cite{Manjon:2010aa}.  This offering consists
of the templated class itkPatchBasedDenoisingImageFilter interfaced through
the DenoiseImage program which includes its own interface program.  We include
a couple of examples.
\end{abstract}

>>>>

% The title should be descriptive enough for people to be able to find
% the relevant document.
\title{A patch-based framework for new ITK functionality:  Joint fusion, denoising,
and non-local super-resolution}

%
% NOTE: This is the last number of the "handle" URL that
% The Insight Journal assigns to your paper as part of the
% submission process. Please replace the number "1338" with
% the actual handle number that you get assigned.
%
\newcommand{\IJhandlerIDnumber}{}

@@

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Nick Tustison$^{1}$ Brian Avants$^{2}$, Long Xie$^{3}$, Paul Yushkevich$^{3}$, and Jose Vicente Manj\'on$^{4}$}
\authoraddress{$^{1}$University of Virginia, Charlottesville, VA\\
               $^{2}$Biogen, Cambridge, MA\\
               $^{3}$University of Pennsylviania, Philadelphia, PA\\
               $^{4}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
               }

@@

% The abstract should be a paragraph or two long, and describe the
% scope of the document.
\begin{abstract}
\noindent
In an earlier Insight Journal article, we introduced an ITK implementation of the
adaptive patch-based image denoising algorithm described in \cite{Manjon:2010aa}.
We follow-up up that offering with a generalized non-local, patch-based ITK class
framework and a refactored denoising class.  In addition, we provide two additional
ITK implementations of related, well-known algorithms.  The first is a non-local
super resolution method described in \cite{Manjon:2010ab,Manjon:2010ac}.  The second is
the multivariate
joint label fusion algorithm of \cite{Wang:2013ab,Wang:2013aa}.  Accompanying these ITK classes are
documented programming interfaces which use our previously introduced unique
command line interface routines.  Several 2-D examples on brain imaging data are
provided to qualitatively demonstrate performance.
\end{abstract}
